Relict populations of a deciduous oak show high resilience to drought despite land-use legacies

### 2018-10-16 man/figures/location_map.Rmd
last update

```{r echo=FALSE, results='asis', eval=show_text}
cat("
# Lista de figuras

- [] Figure 1. Location map

    - [] Ver https://github.com/ajpelu/qpyr_dendro/blob/master/out/fig/geomap/mapa_situacion.pdf

- [] Figure 2. Plot de anomalias
- [] Figure 3. Resilience metrics
- [] Figure 4. BAI chronologies

- [] Figure 5. Residual chronologies --> Supplementary

")
```

@@

![](../../out/fig/geomap/mapa_situacion.jpg){height=600px}

##### 
**Figure 2.** EVI standardized anomaly during the period 2000-2016 for northern and southern populations. Error bars show standard error.

```{r, eval=FALSE}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

drought_years <- c(2005, 2012)

evi_profile_dat_ref <- iv %>% 
  filter(!year %in% drought_years) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = 'reference')

evi_profile_dat_2005 <- iv %>% 
  filter(year == 2005) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = '2005')

evi_profile_dat_2012 <- iv %>% 
  filter(year == 2012) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = '2012')

# Join the three dataframes
evi_profile_compara_dat <- rbind(evi_profile_dat_ref, evi_profile_dat_2005, evi_profile_dat_2012)

# colref <- '#455883'
# colref2 <- '#10253F'
# col2005 <- '#00BA38'
# col2012 <- '#F8766D'

col2012 <- '#0700fe'
col2005 <- '#19e00b'
colref <- '#7b7b7b'

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=1.5, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1))) +
  scale_color_manual(values=c(col2005, col2012, colref))

# profile_compara 
```

```{r}
# From explore_anomalies.Rmd 
# Read data 
anomalias_evimean <- read.csv(here("data/anomalies", "anomalias_evimean.csv"),header = TRUE, sep = ',')

anomalias_evimean <- anomalias_evimean %>% 
  mutate(
    clu_pop = as.factor(case_when(
      pop == 1 ~ "Camarate",
      pop %in% c(2,3,4,5) ~ 'Northern slope',
      pop %in% c(6,7,8) ~ 'Southern slope',
      pop == 9 ~ 'out')),
    clu_pop2 = as.factor(case_when(
      pop %in% c(1,2,3,4,5) ~ 'Northern slope',
      pop %in% c(6,7,8) ~ 'Southern slope',
      pop == 9 ~ 'out'))) %>% 
  filter(clu_pop != 'out')

# colours 
color_neg <- '#a63603'
color_pos <- '#006d2c'

# Standardized Anomalies 
avg_sa_clu <- anomalias_evimean %>% 
  group_by(clu_pop2, y) %>% 
  dplyr::summarise(mean=mean(sa, na.rm=T),
            sd = sd(sa, na.rm=T),
            se = sd/sqrt(length(sa))) %>% 
 mutate(signo = ifelse(mean >= 0, 'pos', 'neg'))

myylab <- 'EVI Standardized Anomaly'

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=16),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1)))

# plot_sa_clu
```

```{r, fig.height=9} 
# grid.arrange(profile_compara, plot_sa_clu)
```

```{r, fig.height=7, eval=FALSE}
a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```

```{r, fig.height=5}
plot_sa_clu 
```

>>>>

@@

![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=600px}
